\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-07-30 jss/article.tex
reference

where $m$ is the number of regression coefficients. As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the second-level mean gets plentiful as the number of groups (\emph{k}) increases. The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, $\{\lambda_{j}\}$, or $\{p_{j}\}$ over 2-level model \citep{2011}, and for posterior propriety under moderate conditions.

>>>>

where $m$ is the number of regression coefficients. As for $\beta$, it is a reasonable choice to assume a flat (non-informative) distribution because information about the second-level mean gets plentiful as the number of groups (\emph{k}) increases. The next flat prior distribution of the second-level variance component $A$ (or $1/r$) is chosen for its good repeated sampling properties for point and interval estimates of the true parameters $\{\mu_{j}\}$, $\{\lambda_{j}\}$, or $\{p_{j}\}$ over 2-level model, and for posterior propriety under moderate conditions \citep{2011}.
